---
title: "runpkg"
output: 
  html_document:
    keep_md: true
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  comment = "#>",
  collapse = TRUE
)
```

An R package for working with [unpkg](https://unpkg.com) -- content delivery network (CDN) for everything on [npm](https://www.npmjs.com/). The goal is to make it easy to find, download, and manage *any file* from any *npm package* in R by storing them as `htmltools::htmlDependency()` objects.

## Installation

**runpkg** is not available on CRAN, but you may install with:

```r
devtools::install_github('cpsievert/runpkg')
```

## Overview

Many npm packages distribute a ['main' file](https://docs.npmjs.com/files/package.json#main) which provides the 'primary entry point to the program'. The `download_main()` function downloads that file and returns a [`htmltools::htmlDependency()`](https://www.rdocumentation.org/packages/htmltools/versions/0.3.6/topics/htmlDependency) object, which makes it easy to incorporate these dependencies in other R projects that leverage **htmltools** (e.g., **shiny** and **htmlwidgets**).

```{r}
library(runpkg)
(jq_main <- download_main("jquery"))

library(htmltools)
cat(renderDependencies(list(jq_main), "href"))
cat(renderDependencies(list(jq_main), "file"))
```

Sometimes you want/need additional files from a package, especially if that package distributes optional dependencies. In this case, you may want to see what other files are distributed with the package via the `ls_()` function:

```{r}
ls_("jquery")
ls_("jquery", "dist")
ls_("jquery@3.2.1", "external/sizzle")
```

Once you've targetted your file(s) of interest, use `download_files()` to acquire those files

```{r}
files <- c(
  "dist/jquery.slim.min.js",
  "external/sizzle/dist/sizzle.min.js"
)
jq_full <- download_files("jquery", files)
cat(renderDependencies(list(jq_full), "file"))
```

## Storing local files

If you need to store your dependencies in a special location, provide a relevant path to the "runpkg.path" option:

```{r}
options(runpkg.path = system.file(package = "runpkg"))
(jq_main <- download_main("jquery"))
cat(renderDependencies(list(jq_main), "file"))
```
